---
title: "Project 3: STAT302package Tutorial"
author: "Jingnan Yuan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Install \texttt{STAT302package} using:
```{r, eval = FALSE}
devtools::install_github("jingnanyuan/STAT302package")
```


```{r setup, massage = FALSE}
library(STAT302package)
library(ggplot2)
```

```{r}
my_t_test(my_gapminder$lifeExp, "two.sided", 60) #p = 0.09322877
my_t_test(my_gapminder$lifeExp, "less", 60) #p = 0.04661438
my_t_test(my_gapminder$lifeExp, "greater", 60) #p = 0.9533856
```
Fail to reject the hypothesis that the mean of life expectancy at birth does not equal to 60.

Reject the hypothesis that the mean of life expectancy at birth is equal to 60.

Fail to reject the hypothesis that the mean of life expectancy at birth does not greater to 60.

```{r}
test <- my_lm(lifeExp ~ gdpPercap + continent, my_gapminder)
test
my_coef <- test[, 1]
my_matrix <- model.matrix(lifeExp ~ gdpPercap + continent, my_gapminder)
y_hat <- my_matrix %*% as.matrix(my_coef)
my_data <- data.frame("Actual" = my_gapminder$lifeExp,
                      "Fitted" = y_hat,
                      "Continent" = my_gapminder$continent)
ggplot(my_data, aes(x = Actual, y = Fitted, color = Continent)) +
  geom_point() + theme_bw(base_size = 20) +
  geom_abline(slope = 1, intercept = 0)
```

The gdpPercap coefficient is 4.45e-04, which shows a weak positive relationship. 

Null hypothiesis: There is no relationship between GDP per capita and life expectancy.

Althernative Hypothesis: There is a significant relationship between GDP per capita and life expectancy.

The p-value of the gdpPercap hypothesis test is 8.552893e-73, which is smaller than 0.05, 
  meaning that we reject the hypothesis that there is no relationship between GDP per capita and life expectancy. 
  It is likely to say that there is a relationship between GDP per capita and life expectancy.

From the plot, we can see there is a positive correlation between Actual and FItted, but it is not perfectly linear, meaning that the model is partially fit.

```{r}
cv_err <- rep(NA, 5)
train_err <- rep(NA, 5)
for (i in 1:10) {
  my_knn <- my_knn_cv(cbind(my_gapminder$gdpPercap, my_gapminder$lifeExp), my_gapminder$continent, i, 5)
    cv_err[i] <- my_knn[[2]]
    train_err[i] <- sum(my_knn$class != my_gapminder$continent)/length(my_gapminder$continent)
}
cbind(cv_err, train_err)
```

I would choose the 10 nearest neighbors model based on the training misclassification rates, and teh 1 nearest neighbors model based on the CV misclassification rates. Above all, I would choose 10 nearest neighbors model since it has the smallest cv error. 

```{r}
mean_error <- rep(NA, 3)
sd_error <- rep(NA, 3)
mse <- matrix(nrow = 3, ncol = 30)
k = c(2, 5, 10)
for (i in 1:3) {
  for (j in 1:30) {
    mse[i,j] <- my_rf_cv(k[i])
  }
  mean_error[i] <- mean(mse[i,])
  sd_error[i] <- sd(mse[i,])
}
my_data <- data.frame("k_Value" = rep(k, 30),
                      "CV_estimated_MSE" = c(mse[1,], mse[2,], mse[3,]))
names(my_data)[2] = "CV_estimated_MSE"
ggplot(my_data, aes(x = k_Value, y = CV_estimated_MSE, group = k_Value)) +
  geom_boxplot() + theme_bw(base_size = 20) +
  labs(x = "k value", y = "CV estimated MSE",
       title = "The CV Estimated MSE by Using Different k Value") 
cbind(mean_error, sd_error)

```

